\documentclass[a4paper,10pt]{article}
\usepackage[english]{babel}
\usepackage[margin=1.8cm]{geometry}
\input{latex/preamble.tex}

\begin{document}

% --------------------------------------
% Header
% --------------------------------------
\begin{center}
    {\LARGE \textbf{Thalys Leite}}\\[2mm]
    São Paulo, Brazil \\[1mm]
    \href{https://thalys.dev}{thalys.dev} \,|\, 
    \href{https://github.com/sylaht}{github.com/sylaht} \,|\, 
    \href{https://www.linkedin.com/in/thalys-leite-94a80a234/}{linkedin.com/in/thalys-leite}\\[2mm]
    \texttt{thalys.leite@email.com}
\end{center}

\vspace{0.3cm}

% --------------------------------------
% Summary
% --------------------------------------
\section*{Summary}
Software engineer with 3 years of experience in frontend and e-commerce solutions, especially VTEX IO.
Skilled in \textbf{JavaScript, TypeScript, React, React Native, Next.js} and \textbf{Node.js}.
Experienced in software architecture, code best practices, performance optimization, cloud environments and Docker.

% --------------------------------------
% Skills
% --------------------------------------
\section*{Skills}
\textbf{Frontend:} JavaScript, TypeScript, React, React Native, Next.js, Angular, CSS, Sass, TailwindCSS, Styled Components\\
\textbf{Backend:} Node.js, Express.js, Fastify\\
\textbf{Databases:} PostgreSQL, MySQL\\
\textbf{DevOps \& Cloud:} Docker, Google Cloud\\
\textbf{Other Languages:} C, C\#, PHP

% --------------------------------------
% Experience
% --------------------------------------
\section*{Experience}
\textbf{Frontend Developer | VTEX IO \& CMS} \hfill 2021 — Present\\[-4pt]
\begin{itemize}[leftmargin=1.2em, noitemsep, topsep=3pt]
    \item Developed and maintained VTEX IO applications, integrating systems and customizing layouts.
    \item Built reusable React + TypeScript components following best practices.
    \item Integrated APIs and developed Node.js backend services.
    \item Collaborated with agile teams (Scrum/Kanban).
    \item Optimized performance and SEO for high-traffic pages.
\end{itemize}

% --------------------------------------
% Education
% --------------------------------------
\section*{Education}
\textbf{Bachelor in Software Engineering} — University [name] \hfill \textit{Ongoing}

% --------------------------------------
% Languages
% --------------------------------------
\section*{Languages}
\begin{itemize}[leftmargin=1.2em, noitemsep, topsep=3pt]
    \item Portuguese: Native
    \item English: Intermediate (technical and professional conversation)
\end{itemize}

% --------------------------------------
% Other Highlights
% --------------------------------------
\section*{Other Highlights}
\begin{itemize}[leftmargin=1.2em, noitemsep, topsep=3pt]
    \item Interest in software engineering, clean architecture, DevOps and distributed systems.
    \item Experience with version control (Git/GitHub Flow) and CI/CD pipelines.
    \item Personal projects with Pub/Sub, Jest and backend automation.
\end{itemize}

\end{document}
